{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-19 thesis/tm.tex
more tm tests

Consider again the program in Figure~\ref{fig:htm-example-reproduced}.
Note that the C-style {\tt x++} operations, when compiled into assembly, %\cite{printy},
results in multiple memory accesses which can be interleaved with other threads.
\[
\begin{tabular}{ll}
	$2a$ & \texttt{temp <- x;} \\
	$2b$ & \texttt{temp <- temp + 1;} \\
	$2c$ & \texttt{x <- temp;} \\
\end{tabular}
\]

@@

			& 2,1	&\cpu{104.37}&\wtm{17.00}&\ints{*6}& \cpu{*43.76}& \wtm{*12.51}& \ints{33}	& \ETA{73} \\
			% TODO: for maximal:
			% 33 interleavings tested; 1 preemptions; job time 4s; pldi time 12326606; new-fixed pldi cputime 43294461
			% 73 brs eta

@@

			& 2,2	&\cpu{ 66.47}&\wtm{*12.42}&\ints{*38}& \cpu{*45.22}& \wtm{15.30}& \ints{85}	& \ETA{860} \\
			& 2,3	&\cpu{ 99.41}&\wtm{*15.92}&\ints{*48}& \cpu{*53.57}& \wtm{21.34}& \ints{217}	& \ETA{9120} \\

@@

@@

			& 2,2 & \ETAdag{qqq}	& \ETAdag{qqq}	&\cpu{16455.24}	& \ints{283756}	& \cpu{1285.06}	& \ints{21684} \\
			& 3,1 & \ETAdag{qqq}	& \ETAdag{qqq}	&\cpu{21153.64}	& \ints{366030}	& \cpu{705.04}	& \ints{12707} \\

>>>>

Consider again the program in Figure~\ref{fig:htm-example-reproduced}.
Note that the C-style {\tt x++} operations, when compiled into assembly, %\cite{printy},
become multiple memory accesses which can be interleaved with other threads.
\[
\begin{tabular}{ll}
	$2a$ & \texttt{temp <- x;} \\
	$2b$ & \texttt{temp <- temp + 1;} \\
	$2c$ & \texttt{x <- temp;} \\
\end{tabular}
\]

@@

			& 2,1	&\cpu{*26.25}&\wtm{*6.42}&\ints{*6}& \cpu{47.80}& \wtm{13.43}& \ints{33}	& \ETA{73} \\
			% using fewer interleavings one for quicksand out of 2 close in cputime bugs
			% 6 interleavings tested; 1 preemptions; job time 4s; pldi time 6415943; new-fixed pldi cputime 26251146
			% 13 interleavings tested; 1 preemptions; job time 3s; pldi time 4654607; new-fixed pldi cputime 16966236
			% 33 interleavings tested; 1 preemptions; job time 4s; pldi time 13430843; new-fixed pldi cputime 47803093

@@

			& 2,2	&\cpu{*18.08}&\wtm{*4.98}&\ints{*10}& \cpu{51.37}& \wtm{16.78}& \ints{85}	& \ETA{860} \\
			% 10 interleavings tested; 1 preemptions; job time 3s; pldi time 4980992; new-fixed pldi cputime 18078134
			% 85 interleavings tested; 1 preemptions; job time 7s; pldi time 16777253; new-fixed pldi cputime 51372309
			& 2,3	&\cpu{*20.93}&\wtm{*5.57}&\ints{*18}& \cpu{57.87}& \wtm{23.99}& \ints{217}	& \ETA{9120} \\
			% 18 interleavings tested; 1 preemptions; job time 4s; pldi time 5573337; new-fixed pldi cputime 20932814
			% 217 interleavings tested; 1 preemptions; job time 15s; pldi time 23987230; new-fixed pldi cputime 57868535

@@

			& 3,1 & \ETAdag{qqq}	& \ETAdag{qqq}	& \ETAdag{qqq}	& \ETAdag{qqq}	&\ETAdag{97y 100d}&\ETAdag{1698185036} \\
			% [JOB 18] progress: 357586/1698185036 brs (0.021057%), ETA 97y 99d 8h 44m 33s (elapsed 9h 59m 41s)

@@

			& 2,2 &\ETAdag{11h 17m}	&\ETAdag{727759}&\cpu{16455.24}	& \ints{283756}	& \cpu{1285.06}	& \ints{21684} \\
			% [JOB 7] progress: 634229/727759 brs (87.148190%), ETA 1h 16m 33s (elapsed 9h 36m 22s)
			% total CPU time consumed: 10h 11s (36011250596 usecs) (core saturation: 12%)
			& 3,1 &\ETAdag{26h 15m}	&\ETAdag{1451708}&\cpu{21153.64}& \ints{366030}	& \cpu{705.04}	& \ints{12707} \\
			% [JOB 5] progress: 655856/1451708 brs (45.178208%), ETA 16h 14m 59s (elapsed 9h 59m 50s)
			% total CPU time consumed: 10h 10s (36010204482 usecs) (core saturation: 12%)
